\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added gmint to intro

First, our approach makes it clear that the defining characteristic of so-called \emph{hierarchical time series} is not aggregation but linear constraints. As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling. Second, we provide a new proof that reconciled forecasts dominate unreconciled forecasts which makes explicit the link between a reconciliation method and a loss function. We believe that this link is lacking in previous work that attempts to establish similar results, in particular \citet{VanErven2015a} and \citet{WicEtAl2019}. Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general. Third, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased. A natural question that arises is what to do in the case of biased reconciled forecasts. Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation. This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.

>>>>

First, our approach makes it clear that the defining characteristic of so-called \emph{hierarchical time series} is not aggregation but linear constraints. As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling. Second, we provide a new proof that reconciled forecasts dominate unreconciled forecasts which makes explicit the link between a reconciliation method and a loss function. We believe that this link is lacking in previous work that attempts to establish similar results, in particular \citet{VanErven2015a} and \citet{WicEtAl2019}. Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general. {\color{blue} Third, we propose a generalised version of MinT that can be tailored to different loss functions.  Recent work by \cite{NysEtAl2019} have proposed special cases of this method, but here we make the distinction  between the role of the loss function and dependence between forecast errors clear, decoupling two concepts that have previously been confounded with one another in the literature.  Fourth}, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased. A natural question that arises is what to do in the case of biased reconciled forecasts. Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation. This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.
